An analysis of interrelations between economic and environmental variables in Australian Winegrowing.

### 2023-10-15 article.tex
done!

What we add is that agricultural economics maybe complex systems that are obfuscated by the expertise of growers to navigate problems such as drought, pests and disease. These systems, although predictable through some variables are not causal. We see this in the evidence of some years notaffecting outcomes even though they are known to contain the aforementioned issues.

@@

\subsection{XGBoosted Trees}
XGBoosted (eXtreme Gradient Boosting) trees were created using the XGBoost library \citep{chenXGBoostScalableTree2016} in the Python Programming language \citep{g.vanrossumPythonTutorialTechnical1995}. XGBoosted trees are a boosted tree ensemble method that can be used to classify classes, or predict continuous response variables. They were chosen for this analysis as the data contained a mixture of class and continuous variables. And, XGBoosted trees are unaffected by multicollinearity, as well as offer high predictive performance for a wide variety of purposes \citep{chenXGBoostScalableTree2016}. An XGBoosted tree was created for each variable to show how they interacted. Each tree included all but the economic variables (operating cost and revenue from grape sales), which were only included within their own trees as response variables. This meant that every variable would have a measure of its importance to other variables (see Section \ref{sec:importance}), which was used to show the highly interrelated nature of variables within vineyards. The complicated interaction between bariables was illustrated using Sankey and Chord diagrams; with variable importance measures being used to show the strength of connection between any two variables (see section \ref{sec:importance}).
\par
Following Chen and Guestrin \citep{chenXGBoostScalableTree2016}, XGboosted trees predict a value $y_i$ from the input $x_i$. The method of prediction is achieved through a tree ensemble model, using $K$ additive functions to predict the output. Each of $f_k$ functions is a classification or regression tree, such that all functions are in the set of all decision trees, given by $\mathcal{F}$, is defined by ${f(x) = \omega_{q(x)}}(q : \mathbb{R}^m \rightarrow T, \omega \in \mathbb{R}^T)$. Where each function corresponds to an independent tree structure $q$ of $\omega$ weights. Each tree has $T$ leaves, which contain a continuous score, represented by $\omega_i$ for the i-th leaf. The final prediction is determined by the sum of the score of the corresponding leaves, given by:
\begin{equation}
 \hat{y_i}=\phi(x_i)=\sum_{k=1}^{K}{f_{k}(x_{i})}, \space f_{K}\in \mathcal{F},
\end{equation}

@@

Regional pressures such as disease and resource access have an incredible influence in determining a vineyard's revenue and operating cost.

The explored relationships between vineyard resource use, operations and geographical properties to revenue and operating costs highlight how discerning regional pressures such as disease,

Several physical parameters such as climate, geography and soil are predetermined by a vineyard's location; making it a widely considered key determinant of grape yield and quality \citep{abbalDecisionSupportSystem2016,agostaRegionalClimateVariability2012,fragaMultivariateClusteringViticultural2017}. 

@@

Warmer regions 
% generally have lower land costs \citep{willchancellorMeasuringAustralianBroadacre2019}, 
are known to be beneficial in hastening the ripening process of winegrapes \citep{webbObservedTrendsWinegrape2011}. Warmer regions are also associated with lower quality grapes, caused largely due to this hastened ripening \citep{botting1996canopy}. In general if irrigated warmer regions have been associated with lower yields due to their generally lower rainfall, which can be mitigated through applying more water \citep{campsGrapeHarvestYield2012}. % FIXME: Rework this sentance
It is likely that the combination of larger vineyards with higher water use is a determining factor in classifying regions which favour larger production of lower quality grapes; reflected through the variables' importance of water use in the XGBoost ensemble. % FIXME: Need to link lower quality to profitability.
% FIXME: Warm inland regions are close to a major source of irrigation water which means that they have always taken advantage of this to grow higher crops. Which are also extremely important to our sector.)
% FIXME: May need to explain that growers are paid @ a $ value / tonne and that the $ value varies in region.
The practice of utilising larger quantities of water for inland Australian wine crops is partly reflected in the prior use of flood style irrigation to saturate soil \citep{bgcoombeGrapeBerryDevelopment2004}. % FIXME: More likely is that they have access to large water licences (Prev used for flood irrigation) That ythey now use on vineyards.
% FIXME: Examples of regions??
This classification can be contrasted with other warmer regions of higher rainfall that use the warmer climate to concentrate their grapes, increasing the flavour profile (and thus quality) \citep{goodwinijeriepRegulatedDeficitIrrigation1992,mgmccarthyEffectCropLoad1986}. This is possibly the connection between the presence of the Hunter Valley within the XGBoost ensemble that determined profit (see Figure \ref{fig:profit_sankey}). With this connection reflecting the restriction of possible strategies employable by winegrowers between different regions. % FIXME:  No this is because the hunter valley/tasmania get paid more / tonne.

@@

In part some winegrowing strategies are restricted simply through access to water resources, being reflected through the region classification tree (see Figure \ref{fig:region_tree}). Regions are likely to have varying access to different water sources, such as those along the River Murray being able to utilise river water for crops, unlike most coastal regions which may be drawing from surgace or underground water. Similarly, the connection between region and fuel use is likely an indicator of the level of infrastructure within the region. Where, the need to pressurise irrigation systems from river water or to generate power would require larger amounts of diesel and petrol. % FIXME: Yes but this requires some explanation

@@

the optimisation of tractor passes % FIXME: What does this mean? Multiple activities with a single pass?
being shown to reduce energy use in vineyards, decreasing running costs, as well as reducing soil compaction \citep{capelloEffectsTractorPasses2019}. 

@@

Decisions made on the ground have far-reaching effects and are difficult to completely capture. A higher number of tractor passes used as a preventative measure for occurrences such as disease, may incur higher operational costs but could be critical in preventing long term losses. With factors such as erosion and soil health being difficult to capture but also influenced by tractor use \citep{capelloEffectsTractorPasses2019,capelloPermanentCoverSoil2020}. Although, performing well in $R^2$, the ability to predict operational costs is limited by the variables incorporated. Reductions in fuel, water and tractor use are obvious methods to reduce operational costs but not necessarily achievable decisions. Without fully capturing more granular activities such as the specifics of what fuel was used for, it is hard to determine what decisions specifically influence the operational costs.

@@

Although less important in the XGBoost ensembles for profit, the variables: cover crops, and number of fungicide spraying and slashing passes are likely linked to broad environmental properties of regions (see Figure \ref{fig:region_sankey} and \ref{fig:profit_sankey}). Rainfall being related to vine fungal growth, disease and weed pressure. With cover crops being an effective and sustainable method to alleviate these issues \citep{delpuechAdaptingCoverCrop2018}. % FIXME: Re-structure this sentance.
It is difficult to extrapolate findings to these methods and the reason for their use due to the broad and varying definition of the regions. Utilising the Geographical Indicator regions defined by Wine Australia \citep{wineaustraliaWineAustraliaOpenData2021} is a limitation, as it is too broad to fully capture a vineyards location and its influence on more granular variables. The reasoning for using approaches such as cover crops can be widely varying. Where, a cover crop may be employed to help increase soil water retention, reduce erosion, increase biodiversity and reduce weeds \citep{capelloEffectsTractorPasses2019,capelloPermanentCoverSoil2020,delpuechAdaptingCoverCrop2018}. However, cover crops can introduce competition with grapevines and may reduce yield depending upon the plants used and the density of the cover crop \citep{goslingLongtermChangesSoil2005,monteiroInfluenceCoverCrop2007}. A more granular definition of region may help to better discern the differences in practices, and the reason for employing them. More sophisticated models, specifically those that utilise expert opinion, may also help to capture and address the decision making process. An example is the optimisation of fungicide sprays using Bayesian models that forecast disease risk \citep{luDiseaseRiskForecasting2020}.

Electricity in particular is used predominantly for irrigation and so is related largely to the size of a vineyard. However, slashing and spraying are measured in discrete tractor passes and show a surprising connection to the overall size of a vineyard, despite not being scaled to any measure of size. This would mean that, although measured as the same increment, a slashing or spraying pass in a larger vineyard would consume more fuel and wages than in a smaller vineyard. % FIXME: May need to maintain bigger vineyards are more likely to have more staff verse small owner operators. Those extra staff may be trying to keep employers busy be sending them slashing (this comment was from Mardi and very hard to validate in the literature.)

It is reasonable that regions, being subjected to different rainfalls and temperatures, would require different amounts of water, and would have access to different water sources. The relation of area harvested and fuel (particularly petrol) is prominent with other predictors. Due to the wide variety of uses of petrol and diesel. It is likely that fuel use is representative of other activities within the vineyard, such as pruning and harvesting. Predictors such as yield and area being highly interconnected to fuel are likely reflective of fuel required to  as they likely operate as proxy variables to other factors, possibly other present variables.

@@

The disparity in accuracy between profit and operational costs is reflective of the complexity in trying to address challenges such as climate change, disease and changing market demands \citep{wineaustraliaNationalVintageReport2020,wineaustraliaNationalVintageReport2021,wineaustraliaNationalVintageReport2022}. The difference between turning a profit or loss is dependent on decisions made and chance. The difference between vineyards that make profit and those that do not could be a multitude of factors including differences in farming practices not captured within this study. Some decisions leading to latent effects such as large scale soil deposition in extreme rain events can be caused by soil compaction due to overworking a vineyard \citep{capelloPermanentCoverSoil2020}.

@@

The causal reasoning behind Revenue and operational costs. The untangling the multicollinearity of these variables.

It maybe better to pursue more causal models and create decision support systems than to model factors directly. It is difficult to untangle the predictive and correlative nature of the variable compared to the causal reasons.

This study has provided valuable insights into the multifaceted dynamics governing operational costs and revenue. 
The impact of different regions highlighted the complex interrelatedness of variables within a vineyard. The paper underscores how factors such as water and fuel intersect to impact operational costs and How different seasonal events affect these operations and the significance of context-specific decision-making. While this investigation utilised a broad regional classification, the potential benefits of adopting a more nuanced approach and incorporating expert knowledge have been highlighted. By delving deeper into the complex interplay of variables, further advancements can be made in optimising vineyard management strategies for lowering operational costs and enhancing sustainability.

>>>>

What we add is that agricultural economics maybe complex systems that are obfuscated by the expertise of growers to navigate problems such as drought, pests and disease. These systems, although predictable through some variables are not causal. We see this in the evidence of some years not affecting outcomes even though they are known to contain the aforementioned issues.

@@

\subsection{XGBoosted Trees}
XGBoosted (eXtreme Gradient Boosting) trees were created using the XGBoost library \citep{chenXGBoostScalableTree2016} in the Python Programming language \citep{g.vanrossumPythonTutorialTechnical1995}. XGBoosted trees are a boosted tree ensemble method that can be used to classify classes, or predict continuous response variables. They were chosen for this analysis as the data contained a mixture of class and continuous variables. And, XGBoosted trees are unaffected by multicollinearity, as well as offer high predictive performance for a wide variety of purposes \citep{chenXGBoostScalableTree2016}. An XGBoosted tree was created for each variable to show how they interacted. Each tree included all but the economic variables (operating cost and revenue from grape sales), which were only included within their own trees as response variables. Separately profit (the difference between revenue and operational costs) was looked at in prior analyses (see appendix) but the results were not included due to low average loss values and model stability. This meant that every variable would have a measure of its importance to other variables (see Section \ref{sec:importance}), which was used to show the highly interrelated nature of variables within vineyards. The complicated interaction between bariables was illustrated using Sankey and Chord diagrams; with variable importance measures being used to show the strength of connection between any two variables (see section \ref{sec:importance}).
\par
Following Chen and Guestrin \citep{chenXGBoostScalableTree2016}, XGboosted trees predict a value $y_i$ from the input $x_i$. The method of prediction is achieved through a tree ensemble model, using $K$ additive functions to predict the output. Each of $f_k$ functions is a classification or regression tree, such that all functions are in the set of all decision trees, given by $\mathcal{F}$, is defined by ${f(x) = \omega_{q(x)}}(q : \mathbb{R}^m \rightarrow T, \omega \in \mathbb{R}^T)$. Where each function corresponds to an independent tree structure $q$ of $\omega$ weights. Each tree has $T$ leaves, which contain a continuous score, represented by $\omega_i$ for the i-th leaf. The final prediction is determined by the sum of the score of the corresponding leaves, given by:
\begin{equation}
 \hat{y_i}=\phi(x_i)=\sum_{k=1}^{K}{f_{k}(x_{i})}, \space f_{K}\in \mathcal{F},
\end{equation}

@@

The explored relationships between vineyard resource use, operations and geographical properties to revenue and operating costs highlight how decisive regional influences can be determining a vineyard's economic outcomes. Several physical parameters such as climate, geography and soil are predetermined by a vineyard's location; making it a widely considered key determinant of grape yield and quality \citep{abbalDecisionSupportSystem2016,agostaRegionalClimateVariability2012,fragaMultivariateClusteringViticultural2017}.

@@

Warmer regions are known to be beneficial in hastening the ripening process of winegrapes \citep{webbObservedTrendsWinegrape2011}. Warmer regions are also associated with lower quality grapes, caused largely due to this hastened ripening \citep{botting1996canopy}. In general warmer regions are not associated with higher yields, but if a vineyard in a warmer region is sufficiently irrigated much higher yields can be achieved than in cooler regions \citep{campsGrapeHarvestYield2012}. It is likely that the combination of larger vineyards with higher water use is a determining factor in classifying regions which favour larger production of grapes; reflected through region using water use so prominently in the XGBoost ensemble. The link to water resources in defining regions is also an important consideration, as vineyards can leverage higher irrigation rates given more accessible water resources. A further consideration in the link between revenue and region is that grape prices are set at a regional level by buyers \citep{wineaustraliaNationalVintageReport2022}. It is also important to consider that some regions carry particular fame regarding the quality of their produce such as Tasmania, the Hunter Valley and Barossa Valley \citep{hallidayAustralianWineEncyclopedia2009}. This classification can be contrasted with other warmer regions of higher rainfall that use the warmer climate to concentrate their grapes, increasing the flavour profile (and thus quality) \citep{goodwinijeriepRegulatedDeficitIrrigation1992,mgmccarthyEffectCropLoad1986}. 
% This is possibly the connection between the presence of the Hunter Valley within the XGBoost ensemble that determined profit (see Figure \ref{fig:profit_sankey}). With this connection reflecting the restriction of possible strategies employable by winegrowers between different regions. % FIXME:  No this is because the hunter valley/tasmania get paid more / tonne.

@@

In part some winegrowing strategies are restricted simply through access to water resources, being reflected through the region classification tree (see Figure \ref{fig:region_tree}). Regions are likely to have varying access to different water sources, such as those along the River Murray being able to utilise river water for crops, unlike most coastal regions which may be drawing from surface or underground water sources. Similarly, the connection between region and fuel use is likely an indicator of the level of infrastructure within the region. Where, the need to pressurise irrigation systems from river water or to generate power would require larger amounts of diesel and petrol.

@@

the optimisation of tractor passes to achieve multiple goals in a pass, being shown to reduce energy use in vineyards, decreasing running costs, as well as reducing soil compaction \citep{capelloEffectsTractorPasses2019}. 

@@

When determining revenue, similar variables were used to operational cost; with region also being of high variable importance relative to other variables (when considering all regions together in importance). It is difficult to extrapolate the specific influence of location on a vineyard's outcomes due to the broad and varying definition of a region. Utilising the Geographical Indicator regions defined by Wine Australia \citep{wineaustraliaWineAustraliaOpenData2021} is a limitation in one way, as it is too broad to fully capture a vineyards location and how that influences variables at a more granular level. However, as buyers set prices at regional levels, it is still important to consider a vineyards Geographical Indicator region. 

@@

Decisions made on the ground have far-reaching effects and are difficult to completely capture. A higher number of tractor passes used as a preventative measure for occurrences such as disease, may incur higher operational costs but could be critical in preventing long term losses. With factors such as erosion and soil health being difficult to capture but also influenced by tractor use \citep{capelloEffectsTractorPasses2019,capelloPermanentCoverSoil2020}. Although, performing well in $R^2$, the ability to predict operational costs is limited by the variables incorporated. Reductions in fuel, water and tractor use are obvious methods to reduce operational costs but not necessarily achievable decisions. Without fully capturing more granular activities such as the specifics of what fuel was used for, it is hard to determine what decisions specifically influence the operational costs. Electricity in particular is used predominantly for irrigation. Size is also a further consideration where slashing and spraying are measured in discrete tractor passes and show a surprising connection to the overall size of a vineyard, despite not being scaled to any measure of size. This would mean that, although measured as the same increment, a slashing or spraying pass in a larger vineyard would consume more fuel and wages than in a smaller vineyard.
The reasoning for any particular decision can be widely varying. 
% Where, a cover crop may be employed to help increase soil water retention, reduce erosion, increase biodiversity and reduce weeds \citep{capelloEffectsTractorPasses2019,capelloPermanentCoverSoil2020,delpuechAdaptingCoverCrop2018}. However, cover crops can introduce competition with grapevines and may reduce yield depending upon the plants used and the density of the cover crop \citep{goslingLongtermChangesSoil2005,monteiroInfluenceCoverCrop2007}. 
A more granular definition of region may help to better discern the differences in practices, and the reason for employing them. More sophisticated models, specifically those that utilise expert opinion, may also help to capture and address the decision-making process. An example is the optimisation of fungicide sprays using Bayesian models that forecast disease risk \citep{luDiseaseRiskForecasting2020}. 
% Although less important in the XGBoost ensembles for profit, the variables: cover crops, and number of fungicide spraying and slashing passes are likely linked to broad environmental properties of regions (see Figure \ref{fig:region_sankey} and \ref{fig:profit_sankey}). Rainfall being related to vine fungal growth, disease and weed pressure. With cover crops being an effective and sustainable method to alleviate these issues \citep{delpuechAdaptingCoverCrop2018}. % FIXME: Re-structure this sentance.

% It is reasonable that regions, being subjected to different rainfalls and temperatures, would require different amounts of water, and would have access to different water sources. The relation of area harvested and fuel (particularly petrol) is prominent with other predictors. Due to the wide variety of uses of petrol and diesel. It is likely that fuel use is representative of other activities within the vineyard, such as pruning and harvesting. Predictors such as yield and area being highly interconnected to fuel are likely reflective of fuel required to  as they likely operate as proxy variables to other factors, possibly other present variables.

@@

Separately revenue and operating cost did have a greater predictability than their counterpart profit. The disparity in accuracy between profit and other economic outcomes is reflective of the complexity in trying to address challenges such as climate change, disease and changing market demands \citep{wineaustraliaNationalVintageReport2020,wineaustraliaNationalVintageReport2021,wineaustraliaNationalVintageReport2022}. The difference between turning a profit or loss is dependent on decisions made and chance. The difference between vineyards that make profit and those that do not could be a multitude of factors including differences in farming practices not captured within this study. Some decisions leading to latent effects such as large scale soil deposition in extreme rain events can be caused by soil compaction due to overworking a vineyard \citep{capelloPermanentCoverSoil2020}.

@@

This study has provided valuable insights into the multifaceted dynamics governing operational costs and revenue. The impact of different regions highlighted the complex interrelatedness of variables within a vineyard. We relate how factors such as water and fuel intersect to impact operational costs and how different seasonal events affect these operations; as well as the significance of context-specific decision-making. While this investigation utilised a broad regional classification, the potential benefits of adopting a more nuanced approach and incorporating expert knowledge have been highlighted. Further work could pursue causal models and the creation of decision support systems. It is difficult to untangle the predictive and correlative nature of a variable compared to the causal reasons. By delving deeper into the complex interplay of variables, further advancements can be made in optimising vineyard management strategies for lowering operational costs and enhancing sustainability.
